Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-07 doc/PRF2022/PRF_main_fig_revis.tex
revised figures

\begin{figure}[h!]
\begin{center}
  \hspace{-1cm}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \hspace{-0.85cm}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation and the inset shows $N_b=60$ particles configuration.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
 Panel (b)--(d) insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
    The black curves are the energies for the $N_b=60$ cases and  
    the red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel A.
    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter. The results of the striated configuration depend on the initial setup.
  }
\end{figure}

@@

The Euclidian distance matrix is the $N_b \times N_b$ matrix 
$[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|$ for $i, j = 1, \dots, N_b$
To measure positional order, we use
\begin{equation}
\label{eq:EDM}
d(t) = \frac{1}{N_b^2}\|D(t) - D(0)\|
\end{equation}
where $\| \cdot \|$ is the Frobeneous norm.
For weak background flow strengths, the deformation in particle
configurations will be relatively small and the collection of
particles behaves as a rigid body i.e., $d(t) \ll 1$.

@@

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$). The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$). The streamlines are plotted in the background.
  }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
  \end{center}
\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases. As expected, the local order parameter drops and the MSD increases. For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_0.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_1.pdf}
  \includegraphics[width=0.22\textwidth]{VTG_Scale_2.pdf} 
    \includegraphics[width=0.22\textwidth]{VTG_Scale_3.pdf}
      \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale_flow} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively. The streamlines are plotted in the background.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
  \end{center}
      \caption{\label{fig:BC2_shear} 
      A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations. Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{MTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{MTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MTG_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_TG_flow} Multi-lamellar stracture in Taylor-Green flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.1, 0.15, 0.2\}$ at $t=600$, respecitively. The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
  \end{center}
    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time. Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively. 
  }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
  \end{center}
\caption{\label{fig:BC3_shear} A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$. The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation. For other two cases, all measures remain nearly constant. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
  \includegraphics[width=0.22\textwidth]{CTG_1.pdf}
  \includegraphics[width=0.22\textwidth]{CTG_2.pdf} 
    \includegraphics[width=0.22\textwidth]{CTG_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG_flow}  A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively. . }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
  \end{center}
\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
  \end{center}
    \caption{\label{fig:BC2_tests} A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$. We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.    }
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation and the inset shows $N_b=60$ particles configuration.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
 Panel (b)--(d) insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} decreases
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
    The black curves are the energies for the $N_b=60$ cases and  
    the red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
    The curve styles are identical to the ones in panel A.
    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter. The results of the striated configuration depend on the initial setup.
  }
\end{figure}

@@

To measure positional order, we use a strain parameter 
\begin{equation}
\label{eq:SP}
E(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \|E_i\|
\end{equation}
where $E_i = \tfrac{1}{2}(F_i^TF_i - I)$ is a Green-Lagrange strain tensor and $F_i$
is an approximate deformation gradient at particle $i$; $\| \cdot \|$ is the Frobeneous norm.
The motivation for  \eqref{eq:SP} is that 
for relatively weak background flow strengths, the near-equilibrium particle
collections behave as a solid and $E(t)$ is close to zero.
More generally, the Green-Lagrange strain tensor $E_i$ 
can be used to encode the energy of elastic deformations from the reference (equilibrium)
to deformed configuration and $E(t)$ gives a sense of how significant these deformations
may be.  Lacking a map from the reference state, 
we approximate a deformation gradient $F_i$ using weighted least squares for the system 
\[
F_i(\aa_j(t) - \aa_i(t)) = \aa_j(0) - \aa_i(0),\quad j = 1,\dots, N_b  
\]
with weights $w_i = \exp(-\|\aa_j(t) - \aa_i(t)\|/4c)$ where $c$ is particle radius.

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$). The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$). The streamlines are plotted in the background.
  }
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases. As expected, the local order parameter drops and the MSD increases. For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale_flow} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.}
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied. The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations. }
\end{figure}

@@

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively. The streamlines are plotted in the background.}
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
  \end{center}
      \caption{\label{fig:BC2_shear} 
      A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$. For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations. Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.}
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_TG_flow} Multi-lamellar stracture in Taylor-Green flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.1, 0.15, 0.2\}$ at $t=600$, respecitively. The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
  \end{center}
    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time. Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively. 
  }
\end{figure}

\begin{figure}
  \begin{center}
  \end{center}
\caption{\label{fig:BC3_shear} A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$. The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation. For other two cases, all measures remain nearly constant. }
\end{figure}

\begin{figure}
  \begin{center}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG_flow}  A striated configuration in shear flows where the streamlines are plotted in the background. Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively. . }
\end{figure}

\begin{figure}
  \begin{center}
  \end{center}
\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
\end{figure}

@@
